\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
missing comma
better wording

%%%%%%%%%%%%%%%%% Tessellated polygons
Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes the ubiquitous being STL and 
more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
deviation distance from the solid decreases the number of polygons increases and hence the memory consumption and execution time of the RTMC simulation.

>>>>

%%%%%%%%%%%%%%%%% Tessellated polygons
Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and 
more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
deviation distance from the solid decreases the number of polygons increases and with it the memory consumption and execution time of the RTMC simulation.
